---
title: "**REPRODUCIBLE RESULTS. Modeling spatiotemporal domestic wastewater variability: Implications to measure sanitation efficiency**"
author: Néstor DelaPaz-Ruíz, Ellen-Wien Augustijn, Mahdi Farnaghi, Raul Zurita-Milla
date: 2022-09-16
output:
  md_document:
    variant: markdown_github
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

#Loading any pre-requirements
#Libraries 
library(knitr)
library(ggplot2)
library(dplyr)
library(reshape2)
library(tidyr)
library(purrr)
library(Rcpp)

#Setup code required
ver.tim <- 0
 
  #source("code/dw.abm.events.into.r.cal.val.1.r")
  #source("code/dw.abm.events.into.r.no.cal.r")
  source("code/dw.abm.validation.snt.before.after.cal.R")

```

Affiliation: Department of Geo-Information Process (GIP),  Faculty of Geo-Information Science and Earth Observation (ITC),  University of Twente,  Drienerlolaan 5, 7522 NB Enschede, The Netherlands

# Model calibration and results of domestic wastewater (DW) variability

# 1. Introduction

This is the documentation to reproduce the sections of calibration and results of the figures 5 and 6.

## 1.1 Problem statement for DW ABM calibration and evaluation

Calibration: The DW ABM model requires suitable input values that produce representative simulated outputs, which are undefined.

Results: The calibrated DW ABM is representative not only for the calibrated day, but also for the evaluation day.

## 1.2 Objective

Calibration: Define calibrated input values that provide simulated results representative of the observed data based on a day of sampled DW pollutants.

Evaluation: Prove that the calibrated DW ABM can reproduce the DW variability of a day outside of the calibration period.

# 2. Domestic wastewater variability: Time series and correlations

## 2.1 Instructions

Before starting, make sure the files that end with `.snt.cal1.csv` exist with `size= 0B` in the path: `"results/calibration.snt/"`. You can assist yourself executing the following code in Git Bash:

```{bash, crete.txt, echo=T, eval=F}
. ./code/newfiles.txt
```

1)  Open the Netlogo files: `dw.sms.abm.snt.2020.cal.val.1.nlogo` & `dw.sms.abm.snt.2020.no.cal.val.1.nlogo`
2)  For each Netlogo file press `ctrl+shift+B` to open the Behavior space menu.
3)  Select and run the experiment: `cal.val.1 (50 runs)` and wait until the simulation concludes.
4)  Execute the below code chucks to obtain the results of the calibration and evaluation based on DW variability analysis.

## 2.2 Results

### 2.2.1 Calibration

Matching simulated and observed DW variability from the WWTP: COD and TSS at multiple time resolutions.

#### **Figure 5.a: Model not calibrated**

Results before calibrating inputs values.

```{r no.cal.plot.cod.cal, echo=FALSE}
val.days.snt <- c("2022-03-22") #Calibration day

#COD WWTP
dwts.dygraph.manhole.cod <- function(
    data,mh.id,tem.res,t.date, poll.sim, poll.obs, poll.sim.ch, poll.obs.ch){
  
  data %>%
    filter(manhole.id == 'wwtp')%>%
    select(date.time, manhole.id, 
           {{poll.sim}}, {{poll.obs}},
           cod.mn,cod.mx)%>%
    filter(str_detect(date.time,t.date))%>%
    pivot_wider(names_from = manhole.id,
                values_from = c({{poll.sim.ch}},{{poll.obs.ch}},
                                cod.mx,cod.mn))%>%
    xts(.,.$date.time)%>%
    dygraph(main = paste (mh.id,
                          tem.res,#wday(t.date,label = TRUE,abbr = TRUE),
                          sep=" - "), #group = t.date,
            width = 400, 
            height = 300)%>% #dyRangeSelector(dateWindow = c("2022-03-22 05:00:00", "2022-03-22 18:00:00"))%>%
    dyOptions(drawPoints = TRUE, useDataTimezone = TRUE,
              pointSize = 1.5)%>%
    dyAxis("y", label = "COD (mg/l)", valueRange = c(-100, 4000)) %>%
    dyAxis("x", label = "Time (hrs)") %>% #, valueRange = c("2022-03-22 07:00:00", "2022-03-22 16:00:00")
    dySeries(c("cod.mn_wwtp","cod.mgl_wwtp","cod.mx_wwtp"), label = "Simulated",color = "#543005")%>%
    dySeries("ob.cod.mgl_wwtp", label = "Observed",color = "#003c30")%>%
    dySeries("date.time", label = " ",color = "white")%>%
    dyLegend(show = "always",
             hideOnMouseOut = FALSE) -> dwplot

    htmltools::tags$div(dwplot, 
                        style = 
                        "padding:5px; 
                        width: 450px;
                        display:inline-block;")
}
 
#TSS WWTP
dwts.dygraph.manhole.tss <- function(
    data,mh.id,tem.res,t.date, poll.sim, poll.obs, poll.sim.ch, poll.obs.ch){

  data %>%
    filter(manhole.id == 'wwtp')%>%
    select(date.time, manhole.id,
           {{poll.sim}}, {{poll.obs}},
           tss.mn,tss.mx)%>%
    filter(str_detect(date.time,t.date))%>%
    pivot_wider(names_from = manhole.id,
                values_from = c({{poll.sim.ch}},{{poll.obs.ch}},
                                tss.mx,tss.mn))%>%
    xts(.,.$date.time)%>%
    dygraph(main = paste (mh.id,#wday(t.date,label = TRUE,abbr = TRUE),
                          tem.res,
                          sep=" - "),#group = t.date,
            width = 400, 
            height = 300)%>%
    dyOptions(drawPoints = TRUE, useDataTimezone = TRUE,
              pointSize = 1.5)%>%
    dyAxis("y", label = "TSS in mg/l", valueRange = c(-100, 4000)) %>%
    dyAxis("x", label = "Time (hrs)") %>%
    dySeries(c("tss.mn_wwtp","tss.mgl_wwtp","tss.mx_wwtp"), label = "Simulated", color = "#7f3b08")%>%
    dySeries("ob.tss.mgl_wwtp", label = "Observed", color = "#2d004b")%>%
    dySeries("date.time", label = " ",color = "white")%>%
    dyLegend(show = "always", hideOnMouseOut = FALSE)  -> dwplot
  
  htmltools::tags$div(dwplot, 
                        style = 
                        "padding:5px; 
                        width: 450px;
                        display:inline-block;")
}

#COD 60 min
val.days.snt %>%
  map(dwts.dygraph.manhole.cod,
      data = no.cal.obs.sim.stn.60min,
      mh.id = 'WWTP',
      tem.res = '60 min',
      poll.sim = cod.mgl,
      poll.obs = ob.cod.mgl,
      poll.sim.ch = 'cod.mgl',
      poll.obs.ch= 'ob.cod.mgl')%>%
  as.list() -> dwplot.list.2.mh

# #COD 30 min
# val.days.snt %>%
#   map(dwts.dygraph.manhole.cod,
#       data = no.cal.obs.sim.stn.30min,
#       mh.id = 'WWTP',
#       tem.res = '30 min',
#       poll.sim = cod.mgl,
#       poll.obs = ob.cod.mgl,
#       poll.sim.ch = 'cod.mgl',
#       poll.obs.ch= 'ob.cod.mgl')%>%
#   as.list() -> dwplot.list.3.mh
# 
# #COD 12 min
# val.days.snt %>%
#   map(dwts.dygraph.manhole.cod,
#       data = no.cal.obs.sim.stn.12min,
#       mh.id = 'WWTP',
#       tem.res = '12 min',
#       poll.sim = cod.mgl,
#       poll.obs = ob.cod.mgl,
#       poll.sim.ch = 'cod.mgl',
#       poll.obs.ch= 'ob.cod.mgl')%>%
#   as.list() -> dwplot.list.4.mh

#TSS 60 min
val.days.snt %>%
  map(dwts.dygraph.manhole.tss,
      data = no.cal.obs.sim.stn.60min,
      mh.id = 'WWTP',
      tem.res = '60 min',
      poll.sim = tss.mgl,
      poll.obs = ob.tss.mgl,
      poll.sim.ch = 'tss.mgl',
      poll.obs.ch= 'ob.tss.mgl')%>%
  as.list() -> dwplot.list.7.mh

# #TSS 30 min
# val.days.snt %>%
#   map(dwts.dygraph.manhole.tss,
#       data = no.cal.obs.sim.stn.30min,
#       mh.id = 'WWTP',
#       tem.res = '30 min',
#       poll.sim = tss.mgl,
#       poll.obs = ob.tss.mgl,
#       poll.sim.ch = 'tss.mgl',
#       poll.obs.ch= 'ob.tss.mgl')%>%
#   as.list() -> dwplot.list.8.mh
# 
# #TSS 12 min
# val.days.snt %>%
#   map(dwts.dygraph.manhole.tss,
#       data = no.cal.obs.sim.stn.12min,
#       mh.id = 'WWTP',
#       tem.res = '12 min',
#       poll.sim = tss.mgl,
#       poll.obs = ob.tss.mgl,
#       poll.sim.ch = 'tss.mgl',
#       poll.obs.ch= 'ob.tss.mgl')%>%
#   as.list() -> dwplot.list.9.mh

htmltools::browsable(htmltools::tagList(dwplot.list.2.mh,dwplot.list.7.mh))


                                        # ,dwplot.list.3.mh,dwplot.list.8.mh,
                                        # dwplot.list.4.mh,dwplot.list.9.mh

```

```{r no.cal.r.cod.cal, echo=FALSE}
#Correlations for calibration
no.cal.tbl.sim.corr.cal.T(paste('corr.tbl.cal.d0',{{ver.tim}}))%>%
  filter(
    Parameter2 == 'cod.mgl',
    manhole.id == 'wwtp',
         res.min	 == 60) %>%
  select(res.min,manhole.id,Parameter1,Parameter2,r.cal.T,p,n_Obs) %>%
  rename(., r.correlation = r.cal.T, 
         WWTP_Catchment = manhole.id)%>%
  kable()
 
# |
#            res.min	 == 30 |
#            res.min	 == 12

```

```{r no.cal.r.tss.cal, echo=FALSE}
#Correlations for calibration 
no.cal.tbl.sim.corr.cal.T(paste('corr.tbl.cal.d0',{{ver.tim}}))%>%
  filter(
    Parameter2 == 'tss.mgl',
    manhole.id == 'wwtp',
         res.min	 == 60) %>%
  select(res.min,manhole.id,Parameter1,Parameter2,r.cal.T,p,n_Obs) %>%
  rename(., r.correlation = r.cal.T, 
         WWTP_Catchment = manhole.id)%>%
  kable()

 # |
 #           res.min	 == 30 |
 #           res.min	 == 12
```

#### **Figure 5.b: Model calibrated**

Results after calibrating inputs values.

```{r plot.cod.cal, echo=FALSE}
val.days.snt <- c("2022-03-22") #Calibration day

#COD WWTP
dwts.dygraph.manhole.cod <- function(
    data,mh.id,tem.res,t.date, poll.sim, poll.obs, poll.sim.ch, poll.obs.ch){
  
  data %>%
    filter(manhole.id == 'wwtp')%>%
    select(date.time, manhole.id, 
           {{poll.sim}}, {{poll.obs}},
           cod.mn,cod.mx)%>%
    filter(str_detect(date.time,t.date))%>%
    pivot_wider(names_from = manhole.id,
                values_from = c({{poll.sim.ch}},{{poll.obs.ch}},
                                cod.mx,cod.mn))%>%
    xts(.,.$date.time)%>%
    dygraph(main = paste (mh.id,
                          tem.res,#wday(t.date,label = TRUE,abbr = TRUE),
                          sep=" - "), #group = t.date,
            width = 400, 
            height = 300)%>% #dyRangeSelector(dateWindow = c("2022-03-22 05:00:00", "2022-03-22 18:00:00"))%>%
    dyOptions(drawPoints = TRUE, useDataTimezone = TRUE,
              pointSize = 1.5)%>%
    dyAxis("y", label = "COD (mg/l)", valueRange = c(-100, 4000)) %>%
    dyAxis("x", label = "Time (hrs)") %>% #, valueRange = c("2022-03-22 07:00:00", "2022-03-22 16:00:00")
    dySeries(c("cod.mn_wwtp","cod.mgl_wwtp","cod.mx_wwtp"), label = "Simulated",color = "#543005")%>%
    dySeries("ob.cod.mgl_wwtp", label = "Observed",color = "#003c30")%>%
    dySeries("date.time", label = " ",color = "white")%>%
    dyLegend(show = "always",
             hideOnMouseOut = FALSE) -> dwplot

    htmltools::tags$div(dwplot, 
                        style = 
                        "padding:5px; 
                        width: 450px;
                        display:inline-block;")
}
 
#TSS WWTP
dwts.dygraph.manhole.tss <- function(
    data,mh.id,tem.res,t.date, poll.sim, poll.obs, poll.sim.ch, poll.obs.ch){

  data %>%
    filter(manhole.id == 'wwtp')%>%
    select(date.time, manhole.id,
           {{poll.sim}}, {{poll.obs}},
           tss.mn,tss.mx)%>%
    filter(str_detect(date.time,t.date))%>%
    pivot_wider(names_from = manhole.id,
                values_from = c({{poll.sim.ch}},{{poll.obs.ch}},
                                tss.mx,tss.mn))%>%
    xts(.,.$date.time)%>%
    dygraph(main = paste (mh.id,#wday(t.date,label = TRUE,abbr = TRUE),
                          tem.res,
                          sep=" - "),#group = t.date,
            width = 400, 
            height = 300)%>%
    dyOptions(drawPoints = TRUE, useDataTimezone = TRUE,
              pointSize = 1.5)%>%
    dyAxis("y", label = "TSS in mg/l", valueRange = c(-100, 4000)) %>%
    dyAxis("x", label = "Time (hrs)") %>%
    dySeries(c("tss.mn_wwtp","tss.mgl_wwtp","tss.mx_wwtp"), label = "Simulated", color = "#7f3b08")%>%
    dySeries("ob.tss.mgl_wwtp", label = "Observed", color = "#2d004b")%>%
    dySeries("date.time", label = " ",color = "white")%>%
    dyLegend(show = "always", hideOnMouseOut = FALSE)  -> dwplot
  
  htmltools::tags$div(dwplot, 
                        style = 
                        "padding:5px; 
                        width: 450px;
                        display:inline-block;")
}

#COD 60 min
val.days.snt %>%
  map(dwts.dygraph.manhole.cod,
      data = obs.sim.stn.60min,
      mh.id = 'WWTP',
      tem.res = '60 min',
      poll.sim = cod.mgl,
      poll.obs = ob.cod.mgl,
      poll.sim.ch = 'cod.mgl',
      poll.obs.ch= 'ob.cod.mgl')%>%
  as.list() -> dwplot.list.2.mh

# #COD 30 min
# val.days.snt %>%
#   map(dwts.dygraph.manhole.cod,
#       data = obs.sim.stn.30min,
#       mh.id = 'WWTP',
#       tem.res = '30 min',
#       poll.sim = cod.mgl,
#       poll.obs = ob.cod.mgl,
#       poll.sim.ch = 'cod.mgl',
#       poll.obs.ch= 'ob.cod.mgl')%>%
#   as.list() -> dwplot.list.3.mh
# 
# #COD 12 min
# val.days.snt %>%
#   map(dwts.dygraph.manhole.cod,
#       data = obs.sim.stn.12min,
#       mh.id = 'WWTP',
#       tem.res = '12 min',
#       poll.sim = cod.mgl,
#       poll.obs = ob.cod.mgl,
#       poll.sim.ch = 'cod.mgl',
#       poll.obs.ch= 'ob.cod.mgl')%>%
#   as.list() -> dwplot.list.4.mh

#TSS 60 min
val.days.snt %>%
  map(dwts.dygraph.manhole.tss,
      data = obs.sim.stn.60min,
      mh.id = 'WWTP',
      tem.res = '60 min',
      poll.sim = tss.mgl,
      poll.obs = ob.tss.mgl,
      poll.sim.ch = 'tss.mgl',
      poll.obs.ch= 'ob.tss.mgl')%>%
  as.list() -> dwplot.list.7.mh

# #TSS 30 min
# val.days.snt %>%
#   map(dwts.dygraph.manhole.tss,
#       data = obs.sim.stn.30min,
#       mh.id = 'WWTP',
#       tem.res = '30 min',
#       poll.sim = tss.mgl,
#       poll.obs = ob.tss.mgl,
#       poll.sim.ch = 'tss.mgl',
#       poll.obs.ch= 'ob.tss.mgl')%>%
#   as.list() -> dwplot.list.8.mh
# 
# #TSS 12 min
# val.days.snt %>%
#   map(dwts.dygraph.manhole.tss,
#       data = obs.sim.stn.12min,
#       mh.id = 'WWTP',
#       tem.res = '12 min',
#       poll.sim = tss.mgl,
#       poll.obs = ob.tss.mgl,
#       poll.sim.ch = 'tss.mgl',
#       poll.obs.ch= 'ob.tss.mgl')%>%
#   as.list() -> dwplot.list.9.mh

htmltools::browsable(htmltools::tagList(dwplot.list.2.mh,dwplot.list.7.mh))

# ,
#                                         dwplot.list.3.mh,dwplot.list.8.mh,
#                                         dwplot.list.4.mh,dwplot.list.9.mh

```

```{r r.cod.cal, echo=FALSE}
#Correlations for calibration day
tbl.sim.corr.cal.T(paste('corr.tbl.cal.d0',{{ver.tim}}))%>%
  filter(
    Parameter2 == 'cod.mgl',
    manhole.id == 'wwtp',
         res.min	 == 60) %>%
  select(res.min,manhole.id,Parameter1,Parameter2,r.cal.T,p,n_Obs) %>%
  rename(., r.correlation = r.cal.T, 
         WWTP_Catchment = manhole.id)%>%
  kable()

 # |
 #           res.min	 == 30 |
 #           res.min	 == 12
```

```{r r.tss.cal, echo=FALSE}
#Correlations for calibration day
tbl.sim.corr.cal.T(paste('corr.tbl.cal.d0',{{ver.tim}}))%>%
  filter(
    Parameter2 == 'tss.mgl',
    manhole.id == 'wwtp',
         res.min	 == 60) %>%
  select(res.min,manhole.id,Parameter1,Parameter2,r.cal.T,p,n_Obs) %>%
  rename(., r.correlation = r.cal.T, 
         WWTP_Catchment = manhole.id)%>%
  kable()

 # |
 #           res.min	 == 30 |
 #           res.min	 == 12
```

### 2.2.2 Evaluation

Confirmation that simulated and observed DW variability match at multiple spatio-temporal resolutions.

This section presents the following evaluations: Evaluation WWTP catchment, COD, TSS at multiple temporal resolutions (60, 30, 12 min). Evaluation catchment 258 at multiple temporal resolutions (60, 30, 12 min). Evaluation catchment 39 at multiple temporal resolutions (60, 30, 12 min).

#### **Figure 6: Model results of domestic wastewater variability**

```{r plot.wwtp.vald1, echo=FALSE}
val.days.snt <- c("2022-03-21") #Evaluation day 1

#COD WWTP
dwts.dygraph.manhole.cod <- function(
    data,tem.res,mh.id,t.date, poll.sim, poll.obs, poll.sim.ch, poll.obs.ch){
  
  data %>%
    filter(manhole.id == 'wwtp')%>%
    select(date.time, manhole.id, 
           {{poll.sim}}, {{poll.obs}},
           cod.mn,cod.mx)%>%
    filter(str_detect(date.time,t.date))%>%
    pivot_wider(names_from = manhole.id,
                values_from = c({{poll.sim.ch}},{{poll.obs.ch}},
                                cod.mx,cod.mn))%>%
    xts(.,.$date.time)%>%
    dygraph(main = paste (#wday(t.date,label = TRUE,abbr = TRUE),
                          mh.id,
                          tem.res,
                          sep=" - "),
            width = 252, 
            height = 230)%>% 
    dyOptions(drawPoints = TRUE, useDataTimezone = TRUE,
              pointSize = 1.5)%>%
    dyAxis("y", label = "COD (mg/l)", valueRange = c(-100, 5000)) %>%
    dyAxis("x", label = "Time (hrs)") %>% 
    dySeries(c("cod.mn_wwtp","cod.mgl_wwtp","cod.mx_wwtp"), label = "Simulated",color = "#543005")%>%
    dySeries("ob.cod.mgl_wwtp", label = "Observed",color = "#003c30")%>%
    dySeries("date.time", label = " ",color = "white")%>%
    dyLegend(show = "always",
             hideOnMouseOut = FALSE) -> dwplot

    htmltools::tags$div(dwplot, 
                        style = 
                        "padding:1px; 
                        width: 252px;
                        display:inline-block;")
}
 
#TSS WWTP
dwts.dygraph.manhole.tss <- function(
    data,tem.res,mh.id,t.date, poll.sim, poll.obs, poll.sim.ch, poll.obs.ch){

  data %>%
    filter(manhole.id == 'wwtp')%>%
    select(date.time, manhole.id,
           {{poll.sim}}, {{poll.obs}},
           tss.mn,tss.mx)%>%
    filter(str_detect(date.time,t.date))%>%
    pivot_wider(names_from = manhole.id,
                values_from = c({{poll.sim.ch}},{{poll.obs.ch}},
                                tss.mx,tss.mn))%>%
    xts(.,.$date.time)%>%
    dygraph(main = paste (
                          mh.id,#wday(t.date,label = TRUE,abbr = TRUE),
                          tem.res,
                          sep=" - "),#group = t.date,
            width = 252, 
            height = 230)%>%
    dyOptions(drawPoints = TRUE, useDataTimezone = TRUE,
              pointSize = 1.5)%>%
    dyAxis("y", label = "TSS in mg/l", valueRange = c(-100, 5000)) %>%
    dyAxis("x", label = "Time (hrs)") %>%
    dySeries(c("tss.mn_wwtp","tss.mgl_wwtp","tss.mx_wwtp"), label = "Simulated", color = "#7f3b08")%>%
    dySeries("ob.tss.mgl_wwtp", label = "Observed", color = "#2d004b")%>%
    dySeries("date.time", label = " ",color = "white")%>%
    dyLegend(show = "always", hideOnMouseOut = FALSE)  -> dwplot
  
  htmltools::tags$div(dwplot, 
                        style = 
                        "padding:1px; 
                        width: 252px;
                        display:inline-block;")
}

#COD 60 min
val.days.snt %>%
  map(dwts.dygraph.manhole.cod,
      data = obs.sim.stn.60min,
      tem.res = '60 min',
      mh.id = 'WWTP',
      poll.sim = cod.mgl,
      poll.obs = ob.cod.mgl,
      poll.sim.ch = 'cod.mgl',
      poll.obs.ch= 'ob.cod.mgl')%>%
  as.list() -> dwplot.list.2.mh

#COD 30 min
val.days.snt %>%
  map(dwts.dygraph.manhole.cod,
      data = obs.sim.stn.30min,
      tem.res = '30 min',
      mh.id = 'WWTP',
      poll.sim = cod.mgl,
      poll.obs = ob.cod.mgl,
      poll.sim.ch = 'cod.mgl',
      poll.obs.ch= 'ob.cod.mgl')%>%
  as.list() -> dwplot.list.3.mh

#COD 12 min
val.days.snt %>%
  map(dwts.dygraph.manhole.cod,
      data = obs.sim.stn.12min,
      tem.res = '12 min',
      mh.id = 'WWTP',
      poll.sim = cod.mgl,
      poll.obs = ob.cod.mgl,
      poll.sim.ch = 'cod.mgl',
      poll.obs.ch= 'ob.cod.mgl')%>%
  as.list() -> dwplot.list.4.mh

#TSS 60 min
val.days.snt %>%
  map(dwts.dygraph.manhole.tss,
      data = obs.sim.stn.60min,
      tem.res = '60 min',
      mh.id = 'WWTP',
      poll.sim = tss.mgl,
      poll.obs = ob.tss.mgl,
      poll.sim.ch = 'tss.mgl',
      poll.obs.ch= 'ob.tss.mgl')%>%
  as.list() -> dwplot.list.7.mh

#TSS 30 min
val.days.snt %>%
  map(dwts.dygraph.manhole.tss,
      data = obs.sim.stn.30min,
      tem.res = '30 min',
      mh.id = 'WWTP',
      poll.sim = tss.mgl,
      poll.obs = ob.tss.mgl,
      poll.sim.ch = 'tss.mgl',
      poll.obs.ch= 'ob.tss.mgl')%>%
  as.list() -> dwplot.list.8.mh

#TSS 12 min
val.days.snt %>%
  map(dwts.dygraph.manhole.tss,
      data = obs.sim.stn.12min,
      tem.res = '12 min',
      mh.id = 'WWTP',
      poll.sim = tss.mgl,
      poll.obs = ob.tss.mgl,
      poll.sim.ch = 'tss.mgl',
      poll.obs.ch= 'ob.tss.mgl')%>%
  as.list() -> dwplot.list.9.mh

htmltools::browsable(htmltools::tagList(
  dwplot.list.2.mh,dwplot.list.3.mh,dwplot.list.4.mh,
  dwplot.list.7.mh,dwplot.list.8.mh,dwplot.list.9.mh))
```

```{r plot.mh258.vald1, echo=FALSE}
val.days.snt <- c("2022-03-21") #Evaluation day 1

#COD 258
dwts.dygraph.manhole.cod <- function(
    data,tem.res,mh.id,t.date, poll.sim, poll.obs, poll.sim.ch, poll.obs.ch){
  
  data %>%
    filter(manhole.id == '258')%>%
    select(date.time, manhole.id, 
           {{poll.sim}}, {{poll.obs}},
           cod.mn,cod.mx)%>%
    filter(str_detect(date.time,t.date))%>%
    pivot_wider(names_from = manhole.id,
                values_from = c({{poll.sim.ch}},{{poll.obs.ch}},
                                cod.mx,cod.mn))%>%
    xts(.,.$date.time)%>%
    dygraph(main = paste (#wday(t.date,label = TRUE,abbr = TRUE),
                          mh.id,
                          tem.res,
                          sep=" - "),
            width = 252, 
            height = 230)%>% 
    dyOptions(drawPoints = TRUE, useDataTimezone = TRUE,
              pointSize = 1.5)%>%
    dyAxis("y", label = "COD (mg/l)", valueRange = c(-100, 5000)) %>%
    dyAxis("x", label = "Time (hrs)") %>% 
    dySeries(c("cod.mn_258","cod.mgl_258","cod.mx_258"), label = "Simulated",color = "#543005")%>%
    dySeries("ob.cod.mgl_258", label = "Observed",color = "#003c30")%>%
    dySeries("date.time", label = " ",color = "white")%>%
    dyLegend(show = "always",
             hideOnMouseOut = FALSE) -> dwplot

    htmltools::tags$div(dwplot, 
                        style = 
                        "padding:1px; 
                        width: 252px;
                        display:inline-block;")
}
 
#TSS 258
dwts.dygraph.manhole.tss <- function(
    data,tem.res,mh.id,t.date, poll.sim, poll.obs, poll.sim.ch, poll.obs.ch){

  data %>%
    filter(manhole.id == '258')%>%
    select(date.time, manhole.id,
           {{poll.sim}}, {{poll.obs}},
           tss.mn,tss.mx)%>%
    filter(str_detect(date.time,t.date))%>%
    pivot_wider(names_from = manhole.id,
                values_from = c({{poll.sim.ch}},{{poll.obs.ch}},
                                tss.mx,tss.mn))%>%
    xts(.,.$date.time)%>%
    dygraph(main = paste (
                          mh.id,#wday(t.date,label = TRUE,abbr = TRUE),
                          tem.res,
                          sep=" - "),#group = t.date,
            width = 252, 
            height = 230)%>%
    dyOptions(drawPoints = TRUE, useDataTimezone = TRUE,
              pointSize = 1.5)%>%
    dyAxis("y", label = "TSS in mg/l", valueRange = c(-100, 5000)) %>%
    dyAxis("x", label = "Time (hrs)") %>%
    dySeries(c("tss.mn_258","tss.mgl_258","tss.mx_258"), label = "Simulated", color = "#7f3b08")%>%
    dySeries("ob.tss.mgl_258", label = "Observed", color = "#2d004b")%>%
    dySeries("date.time", label = " ",color = "white")%>%
    dyLegend(show = "always", hideOnMouseOut = FALSE)  -> dwplot
  
  htmltools::tags$div(dwplot, 
                        style = 
                        "padding:1px; 
                        width: 252px;
                        display:inline-block;")
}

#COD 60 min
val.days.snt %>%
  map(dwts.dygraph.manhole.cod,
      data = obs.sim.stn.60min,
      tem.res = '60 min',
      mh.id = 'mh.258',
      poll.sim = cod.mgl,
      poll.obs = ob.cod.mgl,
      poll.sim.ch = 'cod.mgl',
      poll.obs.ch= 'ob.cod.mgl')%>%
  as.list() -> dwplot.list.2.mh

#COD 30 min
val.days.snt %>%
  map(dwts.dygraph.manhole.cod,
      data = obs.sim.stn.30min,
      tem.res = '30 min',
      mh.id = 'mh.258',
      poll.sim = cod.mgl,
      poll.obs = ob.cod.mgl,
      poll.sim.ch = 'cod.mgl',
      poll.obs.ch= 'ob.cod.mgl')%>%
  as.list() -> dwplot.list.3.mh

#COD 12 min
val.days.snt %>%
  map(dwts.dygraph.manhole.cod,
      data = obs.sim.stn.12min,
      tem.res = '12 min',
      mh.id = 'mh.258',
      poll.sim = cod.mgl,
      poll.obs = ob.cod.mgl,
      poll.sim.ch = 'cod.mgl',
      poll.obs.ch= 'ob.cod.mgl')%>%
  as.list() -> dwplot.list.4.mh

#TSS 60 min
val.days.snt %>%
  map(dwts.dygraph.manhole.tss,
      data = obs.sim.stn.60min,
      tem.res = '60 min',
      mh.id = 'mh.258',
      poll.sim = tss.mgl,
      poll.obs = ob.tss.mgl,
      poll.sim.ch = 'tss.mgl',
      poll.obs.ch= 'ob.tss.mgl')%>%
  as.list() -> dwplot.list.7.mh

#TSS 30 min
val.days.snt %>%
  map(dwts.dygraph.manhole.tss,
      data = obs.sim.stn.30min,
      tem.res = '30 min',
      mh.id = 'mh.258',
      poll.sim = tss.mgl,
      poll.obs = ob.tss.mgl,
      poll.sim.ch = 'tss.mgl',
      poll.obs.ch= 'ob.tss.mgl')%>%
  as.list() -> dwplot.list.8.mh

#TSS 12 min
val.days.snt %>%
  map(dwts.dygraph.manhole.tss,
      data = obs.sim.stn.12min,
      tem.res = '12 min',
      mh.id = 'mh.258',
      poll.sim = tss.mgl,
      poll.obs = ob.tss.mgl,
      poll.sim.ch = 'tss.mgl',
      poll.obs.ch= 'ob.tss.mgl')%>%
  as.list() -> dwplot.list.9.mh

htmltools::browsable(htmltools::tagList(
  dwplot.list.2.mh,dwplot.list.3.mh,dwplot.list.4.mh,
  dwplot.list.7.mh,dwplot.list.8.mh,dwplot.list.9.mh))
```

```{r plot.mh39.vald1, echo=FALSE}
val.days.snt <- c("2022-03-21") #Evaluation day 1

#COD 39
dwts.dygraph.manhole.cod <- function(
    data,tem.res,mh.id,t.date, poll.sim, poll.obs, poll.sim.ch, poll.obs.ch){
  
  data %>%
    filter(manhole.id == '39')%>%
    select(date.time, manhole.id, 
           {{poll.sim}}, {{poll.obs}},
           cod.mn,cod.mx)%>%
    filter(str_detect(date.time,t.date))%>%
    pivot_wider(names_from = manhole.id,
                values_from = c({{poll.sim.ch}},{{poll.obs.ch}},
                                cod.mx,cod.mn))%>%
    xts(.,.$date.time)%>%
    dygraph(main = paste (#wday(t.date,label = TRUE,abbr = TRUE),
                          mh.id,
                          tem.res,
                          sep=" - "),
            width = 252, 
            height = 230)%>% 
    dyOptions(drawPoints = TRUE, useDataTimezone = TRUE,
              pointSize = 1.5)%>%
    dyAxis("y", label = "COD (mg/l)", valueRange = c(-100, 5000)) %>%
    dyAxis("x", label = "Time (hrs)") %>% 
    dySeries(c("cod.mn_39","cod.mgl_39","cod.mx_39"), label = "Simulated",color = "#543005")%>%
    dySeries("ob.cod.mgl_39", label = "Observed",color = "#003c30")%>%
    dySeries("date.time", label = " ",color = "white")%>%
    dyLegend(show = "always",
             hideOnMouseOut = FALSE) -> dwplot

    htmltools::tags$div(dwplot, 
                        style = 
                        "padding:1px; 
                        width: 252px;
                        display:inline-block;")
}
 
#TSS 39
dwts.dygraph.manhole.tss <- function(
    data,tem.res,mh.id,t.date, poll.sim, poll.obs, poll.sim.ch, poll.obs.ch){

  data %>%
    filter(manhole.id == '39')%>%
    select(date.time, manhole.id,
           {{poll.sim}}, {{poll.obs}},
           tss.mn,tss.mx)%>%
    filter(str_detect(date.time,t.date))%>%
    pivot_wider(names_from = manhole.id,
                values_from = c({{poll.sim.ch}},{{poll.obs.ch}},
                                tss.mx,tss.mn))%>%
    xts(.,.$date.time)%>%
    dygraph(main = paste (
                          mh.id,#wday(t.date,label = TRUE,abbr = TRUE),
                          tem.res,
                          sep=" - "),#group = t.date,
            width = 252, 
            height = 230)%>%
    dyOptions(drawPoints = TRUE, useDataTimezone = TRUE,
              pointSize = 1.5)%>%
    dyAxis("y", label = "TSS in mg/l", valueRange = c(-100, 5000)) %>%
    dyAxis("x", label = "Time (hrs)") %>%
    dySeries(c("tss.mn_39","tss.mgl_39","tss.mx_39"), label = "Simulated", color = "#7f3b08")%>%
    dySeries("ob.tss.mgl_39", label = "Observed", color = "#2d004b")%>%
    dySeries("date.time", label = " ",color = "white")%>%
    dyLegend(show = "always", hideOnMouseOut = FALSE)  -> dwplot
  
  htmltools::tags$div(dwplot, 
                        style = 
                        "padding:1px; 
                        width: 252px;
                        display:inline-block;")
}

#COD 60 min
val.days.snt %>%
  map(dwts.dygraph.manhole.cod,
      data = obs.sim.stn.60min,
      tem.res = '60 min',
      mh.id = 'mh.39',
      poll.sim = cod.mgl,
      poll.obs = ob.cod.mgl,
      poll.sim.ch = 'cod.mgl',
      poll.obs.ch= 'ob.cod.mgl')%>%
  as.list() -> dwplot.list.2.mh

#COD 30 min
val.days.snt %>%
  map(dwts.dygraph.manhole.cod,
      data = obs.sim.stn.30min,
      tem.res = '30 min',
      mh.id = 'mh.39',
      poll.sim = cod.mgl,
      poll.obs = ob.cod.mgl,
      poll.sim.ch = 'cod.mgl',
      poll.obs.ch= 'ob.cod.mgl')%>%
  as.list() -> dwplot.list.3.mh

#COD 12 min
val.days.snt %>%
  map(dwts.dygraph.manhole.cod,
      data = obs.sim.stn.12min,
      tem.res = '12 min',
      mh.id = 'mh.39',
      poll.sim = cod.mgl,
      poll.obs = ob.cod.mgl,
      poll.sim.ch = 'cod.mgl',
      poll.obs.ch= 'ob.cod.mgl')%>%
  as.list() -> dwplot.list.4.mh

#TSS 60 min
val.days.snt %>%
  map(dwts.dygraph.manhole.tss,
      data = obs.sim.stn.60min,
      tem.res = '60 min',
      mh.id = 'mh.39',
      poll.sim = tss.mgl,
      poll.obs = ob.tss.mgl,
      poll.sim.ch = 'tss.mgl',
      poll.obs.ch= 'ob.tss.mgl')%>%
  as.list() -> dwplot.list.7.mh

#TSS 30 min
val.days.snt %>%
  map(dwts.dygraph.manhole.tss,
      data = obs.sim.stn.30min,
      tem.res = '30 min',
      mh.id = 'mh.39',
      poll.sim = tss.mgl,
      poll.obs = ob.tss.mgl,
      poll.sim.ch = 'tss.mgl',
      poll.obs.ch= 'ob.tss.mgl')%>%
  as.list() -> dwplot.list.8.mh

#TSS 12 min
val.days.snt %>%
  map(dwts.dygraph.manhole.tss,
      data = obs.sim.stn.12min,
      tem.res = '12 min',
      mh.id = 'mh.39',
      poll.sim = tss.mgl,
      poll.obs = ob.tss.mgl,
      poll.sim.ch = 'tss.mgl',
      poll.obs.ch= 'ob.tss.mgl')%>%
  as.list() -> dwplot.list.9.mh

htmltools::browsable(htmltools::tagList(
  dwplot.list.2.mh,dwplot.list.3.mh,dwplot.list.4.mh,
  dwplot.list.7.mh,dwplot.list.8.mh,dwplot.list.9.mh))
```

#### **Table 2. Metrics to evaluate simulated DW variability**

```{r r.d1.val, echo=FALSE, fig.height = 5, fig.width = 10}
options(scipen=999)
library(kableExtra)
#Correlations for Evaluation day = Monday
#For Evaluation day 1
tbl.sim.corr.val.d1<- function(
    dw.corr.tbl = paste('corr.tbl.val.M',{{ver.tim}})){
  
  z<-rbind(
    as_tibble(vald1.dw.corr.whole(180,obs.sim.stn.180min,'wwtp',"cod.mgl","ob.cod.mgl")),
    as_tibble(vald1.dw.corr.whole(60,obs.sim.stn.60min,'wwtp',"cod.mgl","ob.cod.mgl")),
    as_tibble(vald1.dw.corr.whole(30,obs.sim.stn.30min,'wwtp',"cod.mgl","ob.cod.mgl")),
    as_tibble(vald1.dw.corr.whole(12,obs.sim.stn.12min,'wwtp',"cod.mgl","ob.cod.mgl")),
    as_tibble(vald1.dw.corr.whole(06,obs.sim.stn.06min,'wwtp',"cod.mgl","ob.cod.mgl"))
  )
  
  x<-rbind(
    as_tibble(vald1.dw.corr.whole(180,obs.sim.stn.180min,258,"cod.mgl","ob.cod.mgl")),
    as_tibble(vald1.dw.corr.whole(60,obs.sim.stn.60min,258,"cod.mgl","ob.cod.mgl")),
    as_tibble(vald1.dw.corr.whole(30,obs.sim.stn.30min,258,"cod.mgl","ob.cod.mgl")),
    as_tibble(vald1.dw.corr.whole(12,obs.sim.stn.12min,258,"cod.mgl","ob.cod.mgl")),
    as_tibble(vald1.dw.corr.whole(06,obs.sim.stn.06min,258,"cod.mgl","ob.cod.mgl"))
  )
  
  c<-rbind(
    as_tibble(vald1.dw.corr.whole(180,obs.sim.stn.180min,39,"cod.mgl","ob.cod.mgl")),
    as_tibble(vald1.dw.corr.whole(60,obs.sim.stn.30min,39,"cod.mgl","ob.cod.mgl")),
    as_tibble(vald1.dw.corr.whole(30,obs.sim.stn.30min,39,"cod.mgl","ob.cod.mgl")),
    as_tibble(vald1.dw.corr.whole(12,obs.sim.stn.12min,39,"cod.mgl","ob.cod.mgl")),
    as_tibble(vald1.dw.corr.whole(06,obs.sim.stn.06min,39,"cod.mgl","ob.cod.mgl"))
  )
  
  v<-rbind(
    as_tibble(vald1.dw.corr.whole(180,obs.sim.stn.180min,'wwtp',"tss.mgl","ob.tss.mgl")),
    as_tibble(vald1.dw.corr.whole(60,obs.sim.stn.60min,'wwtp',"tss.mgl","ob.tss.mgl")),
    as_tibble(vald1.dw.corr.whole(30,obs.sim.stn.30min,'wwtp',"tss.mgl","ob.tss.mgl")),
    as_tibble(vald1.dw.corr.whole(12,obs.sim.stn.12min,'wwtp',"tss.mgl","ob.tss.mgl")),
    as_tibble(vald1.dw.corr.whole(06,obs.sim.stn.06min,'wwtp',"tss.mgl","ob.tss.mgl"))
  )
  
  b<-rbind(
    as_tibble(vald1.dw.corr.whole(180,obs.sim.stn.180min,258,"tss.mgl","ob.tss.mgl")),
    as_tibble(vald1.dw.corr.whole(60,obs.sim.stn.60min,258,"tss.mgl","ob.tss.mgl")),
    as_tibble(vald1.dw.corr.whole(30,obs.sim.stn.30min,258,"tss.mgl","ob.tss.mgl")),
    as_tibble(vald1.dw.corr.whole(12,obs.sim.stn.12min,258,"tss.mgl","ob.tss.mgl")),
    as_tibble(vald1.dw.corr.whole(06,obs.sim.stn.06min,258,"tss.mgl","ob.tss.mgl"))
  )
  
  n<-rbind(
    as_tibble(vald1.dw.corr.whole(180,obs.sim.stn.180min,39,"tss.mgl","ob.tss.mgl")),
    as_tibble(vald1.dw.corr.whole(60,obs.sim.stn.60min,39,"tss.mgl","ob.tss.mgl")),
    as_tibble(vald1.dw.corr.whole(30,obs.sim.stn.30min,39,"tss.mgl","ob.tss.mgl")),
    as_tibble(vald1.dw.corr.whole(12,obs.sim.stn.12min,39,"tss.mgl","ob.tss.mgl")),
    as_tibble(vald1.dw.corr.whole(06,obs.sim.stn.06min,39,"tss.mgl","ob.tss.mgl"))
  )
  
  dw.results <- as_tibble(rbind(z,x,c,v,b,n))
  
  #Adding to environment
  assign(dw.corr.tbl,dw.results,envir = globalenv())
  #Storing at folder
  #write_csv(dw.results,paste('results/calibration.snt/',{{ver.tim}},'.corr.tbl.val.d1.csv', sep=""))
  #Show results in console
  dw.results
  
}

tbl.sim.corr.val.d1(paste('corr.tbl.val.d1',{{ver.tim}}))%>%
  mutate(ID = row_number()) %>%
  select(ID,res.min,manhole.id,Parameter2,r.val.M,p,n_Obs)%>%
  filter(manhole.id == "wwtp")%>%
  rename(., 
         WWTP_Catchment = manhole.id,
         resolution.minutes=res.min,
         Pollutant = Parameter2,
         p.value = p, 
         r.correlation = r.val.M
         )%>% kable(., "simple")

tbl.sim.corr.val.d1(paste('corr.tbl.val.d1',{{ver.tim}}))%>%
  mutate(ID = row_number()) %>%
  select(ID,res.min,manhole.id,Parameter2,r.val.M,p,n_Obs)%>%
  filter(manhole.id == 258)%>%
  rename(., 
         Sub.Catchment_258 = manhole.id,
         resolution.minutes=res.min,
         Pollutant = Parameter2,
         p.value = p, 
         r.correlation = r.val.M
         )%>% kable(., "simple")

tbl.sim.corr.val.d1(paste('corr.tbl.val.d1',{{ver.tim}}))%>%
  mutate(ID = row_number()) %>%
  select(ID,res.min,manhole.id,Parameter2,r.val.M,p,n_Obs)%>%
  filter(manhole.id == 39)%>%
  rename(., 
         Sub.Catchment_39 = manhole.id,
         resolution.minutes=res.min,
         Pollutant = Parameter2,
         p.value = p, 
         r.correlation = r.val.M
         )%>% kable(., "simple")

#arrange(desc(r.val.M)) %>%

# %>% kable() -> g
# g

#kable(align = "c")


```

```{r}
installed.packages()[names(sessionInfo()$otherPkgs), "Version"]
```
